Investigation of Limited Detection Schemes for Light Scattering of Optically Trapped Asymmetric Particles

### 2022-12-21 Manuscript_rev2-LL.tex
edits to discussion of prior

The estimate provided by the neural network can be improved further by
accounting for any prior information we know about the dimer. We
therefore, utilise Bayesian inference to update our neural networks
estimation.
\begin{align}
  \label{eq:bayes}
  p(\hat{\bf n}_\alpha| y_k(\hat{\bf s}))
  &=
    \frac{p(y_k(\hat{\bf s})|\hat{\bf n}_\alpha)
    p(\hat{\bf n}_\alpha)}{p(y_k(\hat{\bf s}))}
\end{align}
where $p(\hat{\bf n}_\alpha)$ and $p(y_1, y_2, y_3)$ are the prior estimates of the distributions of particle orientations and instantaneous signals, respectively.
%
Without any prior evidence we assume that the orientation priori of
our dimer $p(\hat{\bf n}_{\alpha})$ is uniform. Knowledge of the dimer
from previous measurement can be used to inform our estimate of
$p(\hat{\bf n}_{\alpha})$, covered in Section~\ref{sec:test}.  The
latter prior $p(y)$ is the probability of measuring a signal
$(y_1, y_2, y_3)$.  This is given by taking the discrete integral over
collection of reference orientations.
\begin{align}
  p(y_1, y_2, y_3)
  =
  \sum_{\alpha=1}^{n_{\rm ref}}
  p(y_1, y_2, y_3|\hat{\bf n}_\alpha)
  p(\hat{\bf n}_\alpha)
\end{align}
From Eq.~\eqref{eq:bayes}, we get a mass probability distribution that
denotes the probability that our dimer is in orientation
$\hat{\bf n}_{\alpha}$ given a signal $(y_1, y_2, y_3)$.  In order to
evaluate the accuracy of our method, we tested it using a Brownian
dynamics simulation of the dimer (see Section~\ref{sec:brownian}).

>>>>

The estimate provided by the neural network can be further improved by
accounting for any prior information known about the dimer orientation
utilizing Bayesian inference:
\begin{align}
  \label{eq:bayes}
  p(\hat{\bf n}_\alpha| y_k(\hat{\bf s}))
  &=
    \frac{p(y_k(\hat{\bf s})|\hat{\bf n}_\alpha)
    p(\hat{\bf n}_\alpha)}{p(y_k(\hat{\bf s}))}
\end{align}
where $p(\hat{\bf n}_\alpha)$ and $p(y_1, y_2, y_3, y_4)$ are the
prior estimates of the distributions of particle orientations and
instantaneous signals, respectively.
%
Without any prior information, we assume that
$p(\hat{\bf n}_{\alpha})$ is uniform.  Knowledge of the dimer
orientation from a previous measurement can be used to inform our
estimate of $p(\hat{\bf n}_{\alpha})$, covered in
Section~\ref{sec:test}.  The latter prior $p(y)$ is the probability of
measuring a signal $(y_1, y_2, y_3, y_4)$.  This is given by taking
the discrete integral over collection of reference orientations.
\begin{align}
  p(y_1, y_2, y_3, y_4)
  =
  \sum_{\alpha=1}^{n_{\rm ref}}
  p(y_1, y_2, y_3, y_4|\hat{\bf n}_\alpha)
  p(\hat{\bf n}_\alpha)
\end{align}
From Eq.~\eqref{eq:bayes}, we get a mass probability distribution that
denotes the probability that our dimer is in orientation
$\hat{\bf n}_{\alpha}$ given a signal $(y_1, y_2, y_3, y_4)$.  In
order to evaluate the accuracy of our method, we tested it using a
Brownian dynamics simulation of the dimer (see
Section~\ref{sec:brownian}).
